\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{grey}

\usepackage[scale=0.8]{geometry}

\setlength{\hintscolumnwidth}{3cm}

\firstname{Thomas}
\familyname{Vo\ss}

\title{Curriculum Vitae}
\address{Sommerladstr. 34}{44795 Bochum}
\phone{+49 (02 34) 6 23 34 88}
\email{me@tvoss.io}
\homepage{https://launchpad.net/~thomas-voss}{https://launchpad.net/$\sim$thomas-voss}
\homepage{https://github.com/vosst}{https://github.com/vosst}

\begin{document}

\makecvtitle

\section{Personal Data}
\cvitem{Date of Birth}{08.08.1980}
\cvitem{Nationality}{German}
\cvitem{Marital Status}{Married, 2 children}

\section{Education}

\cventry{1990--2000}{Abitur}{Theodor-K\"orner Schule}{Bochum}{}{}  % Arguments not required can be left empty
\cventry{2001--2008}{Diploma in computer science, minor in theoretical medicine}{Technische Universit\"at Dortmund}{Dortmund}{}{}
\section{Diploma Thesis}
\cvitem{Title}{Evaluation and Enhancement of the Multi-Objective CMA Evolution Strategy}
\cvitem{Supervisors}{Prof.\ Dr.\ Christian Igel, Prof.\ Dr.\ G\"unter Rudolph}

\section{Work Experience}

\cventry{2001--2004}{Student Assistant}{Materna GmbH}{Dortmund}{}{}
\cventry{2003}{Teaching Assignment: Introduction to Linux \& Unix}{BA Mosbach}{Mosbach}{}{Amount: 93 hours of lectures.}
\cventry{2004--2005}{Research Assistant}{Institute for Neuroinformatics}{Ruhr-University Bochum}{Bochum}{Programming activities.}
\cventry{2005--2008}{Software Engineer}{NISYS GmbH}{Bochum}{}{Design and implementation of software tools for developing advanced driver assistance systems.}
\cventry{2008--10.2011}{CTO, Product Manager NISYS ADAF}{NISYS GmbH}{Bochum}{}{Platform architecture and strategic alignment of the entire tool chain, software quality/life-cycle management}
\cventry{2008--2013}{Project Lead}{Shark Machine Learning Library}{\httplink[http://shark-project.sourceforge.net]{shark-project.sourceforge.net}}{}{Technical lead and organization of overall development activities, implementation of the evolutionary algorithm component.}
\cventry{4.2011--6.2011}{Visiting Scientist}{Max-Planck-Institute for Informatics}{Saarbr\"ucken}{}{Cooperation with Prof.\ Dr.\ Tobias Friedrich on evolutionary multi- and many-objective optimization.}
\cventry{10.2011--6.2012}{Senior Software Engineer}{Canonical Services Ltd.}{Isle of Man}{}{Design, implementation and maintenance of the overall multi-touch infrastructure.}
\cventry{6.2012--4.2013}{Engineering Manager/Tech Lead}{Canonical Services Ltd.}{Isle of Man}{}{Assembled the Mir engineering team, leading it from a small prototyping team to one consisting of 8 full-time engineers. Took over technical lead responsibilities, driving design, implementation and qa efforts during the first year of the project.}
\cventry{4.2013--5.2017}{Ubuntu Senior Technical Architect}{Canonical Services Ltd.}{Isle of Man}{}{
Responsible for the technical architecture of all client-/user-facing aspects of Ubuntu, with a focus on the Ubuntu Phone product. Recently, took over the architecture lead role for Ubuntu Snappy, too. \newline \newline
Designed and implemented infrastructure and concepts throughout the entire OS, including the application life-cycle, low-level facilities to access existing Android drivers and system services, media-processing, positioning and content-sharing middleware as well as user-facing features like Ubuntu scopes. Aligned short-term goals and long-term vision with engineering teams and stakeholders to ensure continuous delivery of high-quality software.}
\cventry{6.2017--present}{Technical Systems Architect}{AirMap Inc.}{Santa Monica, California}{}{
  Responsible for architecting, designing and implementing the core client and core cloud components for delivering and integrating the AirMap services. Advised the \httplink[dronecore.io]{http://dronecore.io} team in terms of architecture and technology choices. \newline \newline
  Rearchitected and reimplemented the existing backend infrastructure with a "cloud-native" mindset, aiming for deployments across all major cloud infrastructure providers while satisfying varying degrees of GDPR requirements leveraging Kubernetes as the underlying orchestrator for executing an Istio/Envoy service mesh talking HTTP1.1/2.0/gRPC. Prepared the platform for planet-scale realtime operations to deliver mission-critical telemetry and traffic updates to drones during flight, and persisting relevant data to a NewSQL database augmented with a high-performance time-series DB. Integrated realtime traffic information from multiple different data providers including radar-data feeds offered by ANSPs.\newline \newline
  Redesigned and reimplemented the core client side component in C++11/14, exposing it to multiple different platforms and runtimes, covering mobile (iOS, Android), desktop (macOS, Windows, Linux) and drone software stacks (Intel Aero).}

\section{Languages}

\cvitemwithcomment{Native language}{German}{Business fluent (both written and verbal)}
\cvitemwithcomment{Foreign language}{English}{Business fluent (both written and verbal)}
\cvitemwithcomment{Foreign language}{French}{Basic knowledge}

\section{Technical Skills}
\cvcomputer{Usage: Unix/Linux}{Excellent}{Dev.: Unix/Linux}{Excellent}
\cvcomputer{Bazaar}{Excellent}{Git}{Very Good}
\cvcomputer{CMake}{Excellent}{Shell scripting}{Good}
\cvcomputer{GCC/GDB}{Excellent}{clang}{Excellent}
\cvcomputer{C/C++(11/14/17)}{Excellent}{Go}{Very good}
\cvcomputer{Java}{Very good}{Python}{Good}
\cvcomputer{Qt/QML}{Excellent}{VTK}{Very Good}
\cvcomputer{boost}{Excellent}{STL}{Exellent}

\section{Miscellaneous}
\cvitem{Erd\"os Number}{3, Paul Erd\"os $\rightarrow$ Joel Spencer $\rightarrow$ Tobias Friedrich $\rightarrow$ Thomas Vo\ss}

\section{Selected Work Samples}
\cvitem{[1]}{Ubuntu platform api, \httplink[http://launchpad.net/platform-api]{launchpad.net/platform-api}}
\cvitem{[2]}{Ubuntu biometryd, \httplink[http://launchpad.net/biometryd]{launchpad.net/biometryd}}
\cvitem{[3]}{Ubuntu trust store, \httplink[http://launchpad.net/trust-store]{launchpad.net/trust-store}}
\cvitem{[4]}{Ubuntu media hub, \httplink[http://launchpad.net/media-hub]{launchpad.net/media-hub}}
\cvitem{[5]}{Ubuntu content hub, \httplink[http://launchpad.net/content-hub]{launchpad.net/content-hub}}
\cvitem{[6]}{Ubuntu location service, \httplink[http://launchpad.net/location-service]{launchpad.net/location-service}}
\cvitem{[7]}{Ubuntu scopes, \httplink[http://launchpad.net/unity-scopes-api]{launchpad.net/unity-scopes-api}}
\cvitem{[8]}{DroneCore, \httplink[http://dronecore.io]{dronecore.io}}
\cvitem{[9]}{Anbox, \httplink[http://anbox.io]{anbox.io}}
\cvitem{[10]}{Fuchsia OS, \httplink[https://fuchsia.googlesource.com]{fuchsia.googlesource.com}}
\section{Selected Publications}
\cvitem{[1]}{Thomas Vo\ss, Nikolaus Hansen, and Christian Igel.\ Recombination for learning strategy
parameters in the MO-CMA-ES. In M.\ Ehrgott, C.\ Fonseca, X.\ Gandibleux, J.-K.\ Hao,
and M.\ Sevaux, editors, Proc.\ 5th International Conference on Evolutionary Multi-Criterion
Optimization (EMO), volume 5467 of LNCS, pages 155--168. Springer-Verlag, 2009.}
\cvitem{[2]}{Thomas Vo\ss, Nikolaus Hansen, and Christian Igel. Improved step size adaptation for the
MO-CMA-ES. In Martin Pelikan and J\"urgen Branke, editors, Proc. 12th Annual Conference
on Genetic and Evolutionary Computation Conference (GECCO), pages 487--494. ACM Press, 2010.}
\cvitem{[3]}{Tobias Friedrich, Karl Bringmann, Thomas Vo\ss, and Christian Igel. The logarithmic
hypervolume indicator. In Hans-Georg Beyer and William B. Langdon, editors, Proc. 11th
International Workshop on Foundations of Genetic Algorithms (FOGA), pages 81--92. ACM
Press, 2011.}
\cvitem{[4]}{Karl Bringmann, Tobias Friedrich, Christian Igel, and Thomas Vo\ss. Speeding up many-objective optimization by Monte Carlo approximations. In Artificial Intelligence, Vol. 204, pages 22--29, 2013.}

\end{document}
